Initial Analysis

### 2019-08-20 Initial_Analysis.Rmd
Updated subseted data
Just moved the analysis to a proper region

write.csv(SubsetData,
          "SubsetData.csv",
          row.names = F)
```

@@

```{r, SOM_Trans_Results, eval = F, echo = F}

Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/Clean_Results.csv") %>% 
  filter(!is.na(Country_Territory))

>>>>

write.csv(SubsetData,
          "SubsetData.csv",
          row.names = F)

###_____________________________ ###

# Loading subsetted data

Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/SubsetData.csv")

@@
